### 2023-03-02 paper/content.tex
Rewrite the simple synthetic section of the paper

\begin{equation}
\begin{aligned}
\sigma_D^2 &= \dfrac{m_y^2\sigma_x^2 + m_x^2\sigma_y^2}{\left(m_x^2 + m_y^2\right)^2} \ , \\
\sigma_I^2 &= \dfrac{m_x^2 m_z^2 \sigma_x^2 + m_y^2 m_z^2 \sigma_y^2 + \left(m_x^2 + m_y^2\right)^2\sigma_z^2}{\left(m_x^2 + m_y^2\right) m^4} \ , \\
\sigma_m^2 &= \dfrac{m_x^2\sigma_x^2 + m_y^2\sigma_y^2 + m_z^2\sigma_z^2}{m^2} \ .
\end{aligned}
\end{equation}

@@

Figure~\ref{fig_synthetic_simple_data}a shows the vertical component of the magnetic field
$b_z$ over a synthetic rock section containing four uniformly magnetized
spherical sources. The map covers a surface of $\qty{1000}{\um} \times
\qty{1000}{\um}$ with
data points in a regular grid of \qty{1}{\um} ($N = 10^6$ observations)
obtained at a sensor-sample distance of \qty{5}{\um}. The magnetic field data is
contaminated with a pseudo-random noise of normal Gaussian distribution with a
zero mean and \qty{20}{\nano\tesla} standard deviation.

We first applied an upward continuation filter to smooth out high-frequency
noise \citep{Blakely1996}, since it strongly affects the first derivatives of
the potential field required by the Euler equation. Then, we calculated the
magnetic total gradient (or horizontal gradient) filter and applied the blob
detection algorithm to the total gradient map to obtain the position of the
data window for each source (Figure~\ref{fig_coordinate_systems}b). The ED was
run for each selected source by assuming the structural index of a
sphere/punctual source, therefore obtaining the Cartesian coordinates of each
source causing the magnetic potential anomaly in the observed data set (Table
1).

\begin{figure}[tb]
\centering
\includegraphics[width=0.75\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
  CAPTION NEEDED
}
\label{fig_synthetic_simple_results}
\end{figure}

The central positions of each source obtained with ED were used as an input
parameter for inverting the vertical magnetic field. The inversion produced a
least squares (or robust) approximation solution for the vector of Cartesian
magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions
(D and I) and intensity of magnetic moment $m$. We also obtained the
uncertainty propagation of this inversion, using Equation (REFERENCE NEEDED)
and considering $\sigma = \qty{15}{\nano\tesla}$.

@@

This test represents a more complex scenario by simulating 100 sources randomly
distributed in the imaged area of a synthetic thin section of 2000 x 1400 $\mu
m$. The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$
spacing and 5 $\mu m$ sample-sensor distance. For greater fidelity to real
samples, the magnetic sources are modeled as spheres with different depths,
radii, and magnetizations. The depths vary between 1 and 19 $\mu m$, while the
radii range from 0.01 to 0.95 $\mu m$. The magnetizations of the sources have
declination and inclination directions sampled from a pseudo-random Gaussian
distribution with a mean of D, I = 45°, 45°, and a standard deviation of 8°.
This randomness simulates the NRM found in real ferromagnetic particles that
vary individually but average out to the inducing field direction. Finally, we
contaminated the data with high-frequency normally-distributed pseudo-random
noise with zero means and 5 nT standard deviations, as well as with
low-frequency noise in the form of additional deep sources beyond the modeling
domain. The noise-corrupted synthetic $b_z$ image is shown in
Figure~\ref{E9td9j9aBB}a.

\begin{figure}[t]
  \centering
  \includegraphics[width=1\linewidth]{figures/ComplexSynthetic.png}
  \caption{
    a) Complex synthetic data contaminated with  both high and low frequencies noise. b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.
  }
  \label{e9td9j9abb}
\end{figure}

The result of the source detection method is shown in Figure~\ref{E9td9j9aBB}b,
where 84 particles out of the original 100 were detected. The spatiality of the
inversion results is one of the key advantages of magnetic microscopy over the
classic techniques of paleomagnetism. Therefore, we present the inversion
results spatially so that we can evaluate any patterns in their distribution.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{figures/ComplexComparison.png}
\caption{
The validation of the result obtained with the inversion was calculated for
each individual particle based on the error between the real parameters modeled
and their respective recovered values, being (a) the direction and (b)
intensity of the magnetic moment, in addition to the R$^2$ score (c) obtained
by comparing the forward model and the actual data. The depth and radius of the
magnetic sources are also important factors that influence the final result,
therefore, these data are given in the form of cross plots, with the vertical
bar represented by the depth (1 - 19 $\\mu m$) and the horizontal bar by the
radius (0.01 - 0.95 $\\mu m$).
}
\label{p8gmj9mwps}
\end{figure}

The application in complex synthetic data allows observing the strengths and
limitations of the proposed methodology. Some of the strengths that can be
mentioned are: (i) the applied technique not only detects most of the modeled
sources but also (ii) most of the recovered magnetic parameters have
considerably low errors, especially in the directions, usually less than 5°
(Figure~\ref{P8gMJ9mWpS}a). (iii) The magnetic moments obtained also tend to
not deviate much from the real values (Figure~\ref{P8gMJ9mWpS}b) when
R\textsuperscript{2} scores are high (\textgreater 0.95)
(Figure~\ref{P8gMJ9mWpS}c). (iv) Shallow particles grouped in clusters are
usually well individualized during window selection, as well as (v) some
particles that produce a weak magnetic signal but isolated particles.

@@

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\linewidth]{figures/ComplexStereo.png}
\caption{
a) Simulation of a thin section of rock with particles uniformly magnetized in
the average direction of the induced field
45{\textbackslash}textdegree/45{\textbackslash}textdegree. b) The recovered
data, without any type of filtering, are sparse, but statistically generate the
same average direction. c) It is still possible to filter only the directions
of the magnetic sources with the best fitting determined by the coefficient of
determination ($R^ 2 \\geq 0.95$) to ensure better grouping of the directions
around the mean value.
}
\label{rds2vueqci}
\end{figure}

>>>>

\begin{equation}
\label{uncertanties}
\begin{aligned}
\sigma_D^2 &= \dfrac{m_y^2\sigma_x^2 + m_x^2\sigma_y^2}{\left(m_x^2 + m_y^2\right)^2} \ , \\
\sigma_I^2 &= \dfrac{m_x^2 m_z^2 \sigma_x^2 + m_y^2 m_z^2 \sigma_y^2 + \left(m_x^2 + m_y^2\right)^2\sigma_z^2}{\left(m_x^2 + m_y^2\right) m^4} \ , \\
\sigma_m^2 &= \dfrac{m_x^2\sigma_x^2 + m_y^2\sigma_y^2 + m_z^2\sigma_z^2}{m^2} \ .
\end{aligned}
\end{equation}

@@

The Figure~\ref{fig_synthetic_simple_data}a shows the vertical component of the magnetic field $b_z$ over a synthetic rock section containing four uniformly magnetized spherical sources. The map covers a surface of $\qty{1000}{\um} \times \qty{1000}{\um}$ with data points in a regular grid of approximate \qty{1}{\um} ($N = 10^6$ observations) obtained at a sensor-sample distance of \qty{5}{\um}. The magnetic field data is contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and \qty{20}{\nano\tesla} standard deviation.

We first applied an upward continuation filter (Fig.~\ref{fig_synthetic_simple_data}b) to smooth out high-frequency noise \citep{Blakely1996}, since it strongly affects the first derivatives of the potential field required by the Euler equation. Then, we calculated the magnetic total gradient anomaly map (Fig.~\ref{fig_synthetic_simple_data}c), which is subjected to a stretch contrast filter to highlight as much as possible the weaker intensity sources (Fig.~\ref{fig_synthetic_simple_data}d), 
in order to facilitate the next step. Subsequently, we applied the blob detection algorithm to the contrasted total gradient map to obtain the position of the data window for each source (Fig.~\ref{fig_synthetic_simple_data}e). The ED was performed for each selected source by assuming the structural index of a sphere/punctual source, therefore obtaining the Cartesian coordinates (Fig.~\ref{fig_synthetic_simple_data}f) of each source causing the magnetic potential anomaly in the observed data set (Table~\ref{tab_synthetic_simple_results}).

\begin{figure}[tb]
\centering
\includegraphics[width=0.6\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
Comparison of true and estimated dipole magnetic moments and directions.
}
\label{fig_synthetic_simple_results}
\end{figure}

The central positions of each source obtained with ED were used as an input parameter for inverting the vertical magnetic field. The inversion produced a least squares approximation solution for the vector of Cartesian
magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions (D and I) and intensity of magnetic moment $m$ (Fig.~\ref{fig_synthetic_simple_results}). We also obtained the uncertainty propagation of this inversion, using equations~\ref{chi_square}-\ref{uncertanties}, as shown in the Table~\ref{tab_synthetic_simple_results}.

@@

This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of 2000 x 2000 $\mu
m$. The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$ spacing and 5 $\mu m$ sample-sensor distance. For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensity. The depths vary between 1 and 20 $\mu m$, while the
magnetic moment intensity range from $10^{-13}$ to $10^{-15}$ $A/m^2$.

To add more complexity, we simulate two stable magnetization  directions, both sampled from a pseudo-random Gaussian distribution, this randomness simulates the NRM found in real ferromagnetic particles that
vary individually but average out to the inducing field direction. The first group of sources ($n = 70$) has a magnetization mean direction of D = 0°, I = 0°, and a standard deviation of 5°. While the second one ($n = 30$) has a magnetization mean direction of D = 180°, I = 0°, and a standard deviation of 5°. Finally, we contaminated the data with high-frequency normally-distributed pseudo-random
noise with zero means and 20 nT standard deviations, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain. The noise-corrupted synthetic $b_z$ image is shown in
Figure~\ref{complex-synthetic-data}a.

\begin{figure}[t]
  \centering
  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
  \caption{
    a) Complex synthetic data contaminated with  both high and low frequencies noise. b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.
  }
  \label{complex-synthetic-data}
\end{figure}

Since now the data have both high and low-frequency noise, we performed a $3^{rd}$ degree polynomial fitting to remove the low-frequency wavelength from the signal. Subsequently, we applied an upward continuation to get rid of the high-frequency ones (Fig.~\ref{complex-synthetic-data}b). Followed by the TGA map calcultaion (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e). The result of the source's window detection method is shown in Figure~\ref{complex-synthetic-data}e,
where 97 particles out of the original 100 were detected.

The spatiality of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism. Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution.

\textbf{FROM HERE!}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\linewidth]{figures/complex-synthetic-comparison.png}
\caption{
The validation of the result obtained with the inversion was calculated for
each individual particle based on the error between the real parameters modeled
and their respective recovered values, being (a) the direction and (b)
intensity of the magnetic moment, in addition to the R$^2$ score (c) obtained
by comparing the forward model and the actual data. The depth and radius of the
magnetic sources are also important factors that influence the final result,
therefore, these data are given in the form of cross plots, with the vertical
bar represented by the depth (1 - 19 $\\mu m$) and the horizontal bar by the
radius (0.01 - 0.95 $\\mu m$).
}
\label{complex-synthetic-comparison}
\end{figure}

The application in complex synthetic data allows observing the strengths and
limitations of the proposed methodology. Some of the strengths that can be
mentioned are: (i) the applied technique not only detects most of the modeled
sources but also (ii) most of the recovered magnetic parameters have
considerably low errors, especially in the directions, usually less than 5°
(Figure~\ref{complex-synthetic-comparison}a). (iii) The magnetic moments obtained also tend to
not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when
R\textsuperscript{2} scores are high (\textgreater 0.95)
(Figure~\ref{complex-synthetic-comparison}c). (iv) Shallow particles grouped in clusters are
usually well individualized during window selection, as well as (v) some
particles that produce a weak magnetic signal but isolated particles.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\linewidth]{figures/complex-synthetic-fitting-test.png}
\caption{
a)
}
\label{complex-synthetic-fitting-test}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\linewidth]{figures/complex-synthetic-stereograms.png}
\caption{
a) Simulation of a thin section of rock with particles uniformly magnetized in
the average direction of the induced field
45{\textbackslash}textdegree/45{\textbackslash}textdegree. b) The recovered
data, without any type of filtering, are sparse, but statistically generate the
same average direction. c) It is still possible to filter only the directions
of the magnetic sources with the best fitting determined by the coefficient of
determination ($R^ 2 \\geq 0.95$) to ensure better grouping of the directions
around the mean value.
}
\label{complex-synthetic-stereograms}
\end{figure}
